---
title: "Caret Package"
author: "Me"
date: "1/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Caret Package

short for Classification And REgression Training. Set of functions that attempt to streamline the process of creating predictive models.

<http://caret.r-forge.r-project.org/>

## Caret functionality

* some preprocessing
    - preProcess
* Data splitting
    - createDataPartition
    - createResample
    - createTimeSlices
* Training/testing functions
    - train
    - predict
* Model comparison
    - confusionMatrix
* Machine learning algorithms in R
    - Linear discriminant analysis
    - Regression
    - Naive Bayes
    - Support vector machines
    - Classification and regression trees
    - Random forests
    - Boosting
    - etc
    
| obj Class | Package | predict Function Syntax |
|-----------|---------|---|
| lda | MASS | predict(obj) (no options needed)|
| glm | stats | predict(obj,type = "response") |
| gbm | gbm | predict(obj, type = "response", n.trees) |
| mda | mda | predict(obj, type = "posterior") |
| rpart | rpart | predict(obj, type = "prob") |
| Weka | RWeka | predict(obj, type = "probability") |
| LogitBoost | caTools | predict(obj, type = "raw", nIter) |

```{r, warning=F}
library(caret);library(kernlab);data(spam)
inTrain <- createDataPartition(y=spam$type, p=0.75,list=F)
training <- spam[inTrain,]
testing <- spam[-inTrain,]
dim(training)
```

## SPAM Example: Fit a model

```{r, warning=F}
set.seed(32343)
modelFit <- train(type ~., data=training, method="glm")
modelFit
```


```{r}
predictions <- predict(modelFit,newdata = testing)
confusionMatrix(predictions,testing$type)
```

## SPAM Example: data splitting with K-fold

```{r}
#returns training set
folds <- createFolds(y=spam$type, k=10, list=T, returnTrain = T);
#returns test set
folds_test <- createFolds(y=spam$type, k=10, list=T, returnTrain = F);
sapply(folds,length);
sapply(folds_test,length);
folds[[1]][1:10]
```

## SPAM Example: Resampling

```{r}
folds <- createResample(y = spam$type, times = 10, list=T)
sapply(folds,length)
folds[[1]][1:10]
```

## SPAM Example: Time Slices

```{r}
tme <- 1:1000
folds <- createTimeSlices(y=tme,initialWindow = 20, horizon = 10)
names(folds)
folds$train[[1]]
folds$test[[1]]
```

* Caret tutorials:
    - <http://www.edii.uclm.es/~useR-2013/Tutorials/kuhn/user_caret_2up.pdf>
    - <http://cran.r-project.org/web/packages/caret/vignettes/caret.pdf>
* Paper introducing the caret package
    - <http://www.jstatsoft.org/v28/i05/paper>
    
## Train options

```{r}
args(trainControl)
```

## trainControl resampling

* method
    - boot = bootstrapping
    - boot632 = bootstrapping with adjustment
    - cv = cross validation
    - repeatedcv = repeated cross validation
    - LOOCV = leave one out cross validation
* number
    - for boot/cross validation
    - Number of subsamples to take
* repeats
    - number of times to repeat subsampling
    - if big this can slow things down

## Setting the seed

* it is often useful to set an overall seed
* you can also set a seed for each resample
* seeding each resample is useful for parallel fits
