---
title: "My Presentation"
author: "Me"
date: "11/5/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My First Map
```{r, echo=FALSE}
library(leaflet)
df = data.frame(lat = runif(20, min = 39.2, max = 39.3),
                lng = runif(20, min = -76.6, max = -76.5))
my_map = df %>% leaflet() %>% addTiles() %>% addCircleMarkers()
my_map
```

## My New Slide
some comments

*italics*

**bold**
`for (i %in% 1:10)`

```{r, comment="", echo=TRUE}
head(mtcars)
```


## My Title

- Bullet one
- Bullet two

1. Item a
2. Item b

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

